My title

### 2024-03-11 paper/paper.qmd
edit graph name

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
```

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false
toronto_shelters_clean |>
  drop_na(occupied_rooms, sector, location_city) |>
  ggplot(aes(x = location_city, y = occupied_rooms, color = sector)) +
  geom_point() +
  theme_minimal() +
  labs(x = "location_city", y = "occupied_rooms", color = "Sector") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false
toronto_shelters_clean |>
  drop_na(location_city) |>
  ggplot(mapping = aes(x = location_city, fill = sector)) +
  geom_bar() +
  theme_linedraw() +
  labs(x = "location_city",y = "num_occupied_rooms",fill = "sector") +
  facet_wrap(vars(program_model), scales = "free") +
  guides(x = guide_axis(angle = 60)) +
  theme(legend.position = "bottom") + 
  scale_fill_viridis_d(option = "magma")
```

@@

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

>>>>

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
library(bayesplot)
library(rstanarm)

```

@@

Some of our data is of penguins (@fig-room_occupancy), from @palmerpenguins.

```{r}
#| label: fig-room_occupancy
#| fig-cap: Monthly Average Occupancy of Shelter Rooms in Toronto, 2022
#| echo: false

@@

```{r}
#| label: fig-across_cities
#| fig-cap: Occupancy of Shelter Rooms by Sector Across Toronto Cities
#| echo: false
#| warning: false
#| message: false
toronto_shelters_clean |>
  drop_na(occupied_rooms, sector, location_city) |>
  ggplot(aes(x = location_city, y = occupied_rooms, color = sector)) +
  geom_point() +
  theme_minimal() +
  labs(x = "location_city", y = "occupied_rooms", color = "Sector") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-by_sector
#| fig-cap: Comparative Analysis of Shelter Room Occupancy by Sector and Program Model Across Toronto Cities
#| echo: false
#| warning: false
#| message: false
toronto_shelters_clean |>
  drop_na(location_city) |>
  ggplot(mapping = aes(x = location_city, fill = sector)) +
  geom_bar() +
  theme_linedraw() +
  labs(x = "location_city",y = "num_occupied_rooms",fill = "sector") +
  facet_wrap(vars(program_model), scales = "free") +
  guides(x = guide_axis(angle = 60)) +
  theme(legend.position = "bottom") + 
  scale_fill_viridis_d(option = "magma")
```

@@

And also planes (@fig-by_sector). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
